---
title: "Assignemnt 2"
author: "Faizan Younus"
date: "9/9/2018"
output:
  html_document: default
  pdf_document: default
---


Choose six recent popular movies.  Ask at least five people that you know (friends, family, classmates, imaginary friends) to rate each of these movie that they have seen on a scale of 1 to 5.  Take the results (observations) and store them in a SQL database.  Load the information into an R dataframe.

Your deliverables should include your SQL scripts and your R Markdown code, posted to GitHub.



SQL Code:
DROP DATABASE IF EXISTS movie;
CREATE database movie;


CREATE TABLE users (userID int not null auto_increment, 
firstname varchar(20),
lastname varchar(20),
primary key (userID));


INSERT INTO users (firstname, lastname) VALUES
('Fawad','Younus'),
('Saad','Younus'),
('Mariam','Shabbir'),
('Wajidul','Hussain'),
('Atib','Ali');

CREATE TABLE movies (
movieID int not null auto_increment,
title varchar (30),
genre varchar(20),
RottenTom float,
primary key (movieID));


INSERT INTO movies (title, genre, RottenTom) VALUES
('Crazy Rich Asians','Action',9.3),
('The Meg','Action',4.6),
('Mission Impossible','Action',9.7),
('Christopher Robin','Family',7.0),
('The Nun','Horror',2.8),
('Incredibles 2','Animation',9.4);

 
CREATE TABLE reviews(
userID int,
movieID int,
userrating int);

INSERT INTO reviews (userID, movieID, userrating) VALUES
(1,1,4),(1,2,4),(1,3,3),(1,4,4),(1,5,4),(1,6,5),
(2,1,3),(2,2,3),(2,3,2),(2,4,5),(2,5,5),(2,6,3),
(3,1,5),(3,2,5),(3,3,5),(3,4,4),(3,5,5),(3,6,3),
(4,1,4),(4,2,3),(4,3,2),(4,4,2),(4,5,4),(4,6,3),
(5,1,5),(5,2,3),(5,3,3),(5,4,4),(5,5,4),(5,6,3);

SELECT users.firstname, users.lastname, movies.title, movies.genre, movies.RottenTom, reviews.userrating from reviews
JOIN users on users.userID = reviews.userID
JOIN movies on reviews.movieID = movies.movieID
ORDER BY title;




Load Library
```{r}
library(RMySQL)
```


Pulling SQL database into R studio:
```{r}
rmysql.settingsfile<-"/etc/my.cnf"
con <- dbConnect(RMySQL::MySQL(), default.file=rmysql.settingsfile, dbname = "sys", username='root', password='Veloster76')
sql <- "SELECT users.firstname, users.lastname, movies.title, movies.genre, movies.RottenTom, reviews.userrating from reviews JOIN users on users.userID = reviews.userID JOIN movies on reviews.movieID = movies.movieID ORDER BY title;"
res <- dbGetQuery(con, sql)
res
```


Mean of reviews vs RT:
```{r}
View1=aggregate(res[, 6], list(res$title, res$RottenTom), mean)
colnames(View1) <- c("Move_Title", "User_Rank","RT_Rank")
View1
```

